Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-25 paper/paper.tex
made the side margins 1.25 from 1.5, and re-arranged a handful of figures to straighten things out. should have plenty of room now

\documentclass[pdftex,10pt,letter]{article}
\usepackage[pdftex]{graphicx}
\usepackage[left=1.5in, right=1.5in, top=1.25in, bottom=1.25in]{geometry}
\usepackage{hyperref}
\hypersetup{ colorlinks=true
           , linkcolor=blue
           , pdfnewwindow=true 
           }
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{wrapfig}
\usepackage{listings}
\usepackage{float}
\usepackage{textcomp}
\usepackage{multicol}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand{\itemspace}{	\setlength{\itemsep}{0cm} \setlength{\parskip}{0cm}}
\newcommand{\degrees}[1]
{
\begin{math}
#1^{\circ} 
\end{math}
}
\hyphenation{auto-nomous construction}

@@

\newpage
\subsection{Airframe}

\subsubsection{Daedalus}
\begin{wrapfigure}{l}{0.5\textwidth}
	\includegraphics[width=0.47\textwidth]{../images/daedalus_isometric.jpg}
	\caption{The \emph{Daedalus}}
	\label{fig:daedalus}
\end{wrapfigure}
Louis Stumpf, a member of our local R/C club, donated a 10ft 1in (3.07m) wingspan, 7ft 8in (2.33m) long, high wing trainer to our club. It met all of the requirements outlined previously.

The plane, first built out of foam and balsa from long-lost plans in 1986, was accepted graciously, but required quite a bit of work before it was once again flight-worthy. We removed the covering to find water damage and rot which resulted from years of storage. We stripped and rebuilt nearly the entire airframe, adding carbon-fiber reinforcements to the wing in anticipation of increased wing loading due to our payload. Once rebuilt and covered,  the \emph{Daedalus} weighed 19.5 lbs with engine. A full 24oz fuel tank, plus 4lbs electronics payload, would bring the maximum takeoff weight to 25lbs.

We wanted to certify the wings and wing root would withstand large dynamic forces in flight. 
We designed a test to mimic the 
Federal Airworthiness Standards' structural requirements\footnote{Special Federal Aviation Regulation No. 23, Subpart C--Structure. Assuming full load on wing as described in 23.335 paragraph 4.i., where an aircraft must pull out of a \degrees{7.5} dive at cruise velocity and cruise power ``with a load factor of 1.5 (0.5$g$. acceleration increment)'' \cite{far23}}. Our first test was designed to certify that the wing, supported at the wing root and fuselage, could take a bottom loading present in a 1.5$g$ acceleration, with a safety factor of 1.5\footnote{As stated in 23.303 \cite{far23}.}.

@@

\subsubsection{Knight Two}
\begin{wrapfigure}{r}{0.4\textwidth}
	\centering
	\subfloat[The unfinished \emph{Knight Two}]{\label{fig:knighttwo_construction} 
			\includegraphics[width=0.37\textwidth]{../images/knighttwo_uncovered_outdoors.jpg}}
\\
	\subfloat[A completed 12 Foot Telemaster. Photo Credit: Hobby Lobby] {\label{fig:knighttwo_12ft_telemaster} 
			\includegraphics[width=0.37\textwidth]{../images/telemaster_12ft_hobbylobby.jpg}}
  	\label{fig:knighttwo}
  	\caption[Knight Two]{Knight Two}

\end{wrapfigure}

@@

\newpage
\section{Autopilot}
Our entry uses an autopilot system based off the open source Paparazzi project \cite{paparazziweb}. We ported the airborne code to Linux in order to use a single computer for all of our flight hardware and software.

\subsection{Hardware}
\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{../images/hardware_conn_diagram.pdf}
	\caption{Hardware connection diagram for the autopilot and imaging systems. Only one of the 9 axis AHRS and Thermopile Attitude Sensor are used.}
	\label{fig:hardware_conn_diagram}
\end{figure}

@@

Thanks to sensor donations from Invensense and ST Micro, we were able to build a 9 axis Attitude and Heading Reference Sensor (AHRS) from an Invensense ITG-3200 3-axis rate gyro \cite{itg3200} and an ST Micro LSM303DLH 3-axis accelerometer and magnetometer. \cite{lsm303dlh}

@@

The pan servo is calibrated before installation by mapping servo PWM inputs to a measured angular output at \degrees{30} intervals. Linear interpolation is used to determine PWM outputs which achieve intermediate angles. The tilt servo is calibrated at \degrees{10} intervals, due to its much smaller rotation range. As shown in Figure \ref{fig:pantilt_linkplots}, the angular acceleration of the camera angle linkage (Alpha4) is almost constant compared to the servo arm linkage throughout the range $[0^{\circ}, 135^{\circ}]$. The linkage has been designed to keep the majority of nonlinear rotation outside the camera's range of rotation. Therefore, we can consider the calibrated servo output to be directly related to the camera angle.  The endpoints of the tilt rotation rang are calibrated and enforced in software, because pushing the camera outside this range may damage it.
\newpage
\subsection{Obtaining Images}

>>>>

\documentclass[pdftex,10pt,letter]{article}
\usepackage[pdftex]{graphicx}
\usepackage[left=1.25in, right=1.25in, top=1.25in, bottom=1.25in]{geometry}
\usepackage{hyperref}
\hypersetup{ colorlinks=true
           , linkcolor=blue
           , pdfnewwindow=true 
           }
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{wrapfig}
\usepackage{listings}
\usepackage{float}
\usepackage{textcomp}
\usepackage{multicol}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand{\itemspace}{	\setlength{\itemsep}{0cm} \setlength{\parskip}{0cm}}
\newcommand{\degrees}[1]
{
\begin{math}
#1^{\circ} 
\end{math}
}
\hyphenation{auto-nomous construction}

@@

\subsection{Airframe}

\subsubsection{Daedalus}

Louis Stumpf, a member of our local R/C club, donated a 10ft 1in (3.07m) wingspan, 7ft 8in (2.33m) long, high wing trainer to our club. It met all of the requirements outlined previously.

The plane, first built out of foam and balsa from long-lost plans in 1986, was accepted graciously, but required quite a bit of work before it was once again flight-worthy. We removed the covering to find water damage and rot which resulted from years of storage. We stripped and rebuilt nearly the entire airframe, adding carbon-fiber reinforcements to the wing in anticipation of increased wing loading due to our payload. Once rebuilt and covered,  the \emph{Daedalus} weighed 19.5 lbs with engine. A full 24oz fuel tank, plus 4lbs electronics payload, would bring the maximum takeoff weight to 25lbs.
\begin{wrapfigure}{l}{0.5\textwidth}
	\includegraphics[width=0.47\textwidth]{../images/daedalus_isometric.jpg}
	\caption{The \emph{Daedalus}}
	\label{fig:daedalus}
\end{wrapfigure}
We wanted to certify the wings and wing root would withstand large dynamic forces in flight. 
We designed a test to mimic the 
Federal Airworthiness Standards' structural requirements\footnote{Special Federal Aviation Regulation No. 23, Subpart C--Structure. Assuming full load on wing as described in 23.335 paragraph 4.i., where an aircraft must pull out of a \degrees{7.5} dive at cruise velocity and cruise power ``with a load factor of 1.5 (0.5$g$. acceleration increment)'' \cite{far23}}. Our first test was designed to certify that the wing, supported at the wing root and fuselage, could take a bottom loading present in a 1.5$g$ acceleration, with a safety factor of 1.5\footnote{As stated in 23.303 \cite{far23}.}.

@@

\subsubsection{Knight Two}
\begin{figure}
	\centering
	\subfloat[The unfinished \emph{Knight Two}]{\label{fig:knighttwo_construction} 
			\includegraphics[width=0.37\textwidth]{../images/knighttwo_uncovered_outdoors.jpg}}
	\subfloat[A completed 12 Foot Telemaster. Photo Credit: Hobby Lobby] {\label{fig:knighttwo_12ft_telemaster} 
			\includegraphics[width=0.37\textwidth]{../images/telemaster_12ft_hobbylobby.jpg}}
  	\label{fig:knighttwo}
  	\caption[Knight Two]{Knight Two}

\end{figure}

@@

\section{Autopilot}
Our entry uses an autopilot system based off the open source Paparazzi project \cite{paparazziweb}. We ported the airborne code to Linux in order to use a single computer for all of our flight hardware and software.

\subsection{Hardware}
\begin{figure}[t]
	\centering
	\includegraphics[width=0.9\textwidth]{../images/hardware_conn_diagram.pdf}
	\caption{Hardware connection diagram for the autopilot and imaging systems. Only one of the 9 axis AHRS and Thermopile Attitude Sensor are used.}
	\label{fig:hardware_conn_diagram}
\end{figure}

@@

Thanks to sensor donations from Invensense and ST Micro, we were able to build a 9 axis Attitude and Heading Reference Sensor (AHRS) from an Invensense ITG-3200 3-axis rate gyro \cite{itg3200} and an ST Micro LSM303DLH 3-axis accelerometer and magnetometer \cite{lsm303dlh}.

@@

The pan servo is calibrated before installation by mapping servo PWM inputs to a measured angular output at \degrees{30} intervals. Linear interpolation is used to determine PWM outputs which achieve intermediate angles. The tilt servo is calibrated at \degrees{10} intervals, due to its much smaller rotation range. As shown in Figure \ref{fig:pantilt_linkplots}, the angular acceleration of the camera angle linkage (Alpha4) is almost constant compared to the servo arm linkage throughout the range $[0^{\circ}, 135^{\circ}]$. The linkage has been designed to keep the majority of nonlinear rotation outside the camera's range of rotation. Therefore, we can consider the calibrated servo output to be directly related to the camera angle.  The endpoints of the tilt rotation rang are calibrated and enforced in software, because pushing the camera outside this range may damage it.

\subsection{Obtaining Images}
